APPM 3310 Project\\\Large{Static Analysis of Truss Systems}

### 2016-04-26 paper.tex
Add Discussion section from Ryan Marizza.

>>>>

Truss analysis using DSM ignores many real world phenomena and has many
limitations in terms of complexity for the sake of simplicity. A more
realistic, yet much more complicated FEM tool could be created to analyze a
truss system taking into account more real world phenomena and allowing for
much more information to be imputed about the truss system. Such
simplifications that are made by the DSM analysis are as follows: friction is
ignored, the bending of truss members is ignored, the cross sectional area of
each truss element is assumed to be constant, nodes do not impart torque on
elements, and forces can only be applied at nodes. Understanding of FEM could
be furthered by creating a more realistic truss system analyzer that takes
these phenomena into account and allows for forces to be applied at non-node
locations.
